Taking Linear Logic Apart

### 2018-04-23 doc/tlla2018/main.tex
Minor corrections

  Reductions can be constructed as using the rules from \cref{def:cp-reduction},
  with the following changes:

@@

\begin{theorem}\label{thm:hcp2cp-bigtens}
  If $\seq{\mathcal{G}}$ in \hcp, then $\seq{\bigtens\mathcal{G}}$ in \cp.
\end{theorem}
\begin{proof}
  By case analysis on the structure of the hyper-environment $\ty{\mathcal{G}}$.
  \begin{itemize}
  \item
    If $\ty{\mathcal{G}} = \ty{\emptyhypercontext}$, we apply $(\one)$.
  \item
    If $\ty{\mathcal{G}} = \ty{\Gamma_1 \hsep \dots \hsep \Gamma_n}$,
    we apply \cref{lem:hcp2cp-split} to obtain proofs of $\seq{\Gamma_1}, \dots,
    \seq{\Gamma_n}$ in \cp, then we apply \cref{lem:cp-bigparr} to each of
    those proofs to obtain proofs of $\seq{\bigparr\Gamma_1}, \dots,
    \seq{\bigparr\Gamma_n}$, and join them using $(\tens)$ to obtain a single
    proof of $\seq{\bigtens\mathcal{G}}$ in \cp.
  \end{itemize}
\end{proof}

>>>>

  Reductions can only be constructed as follows:

@@

\begin{theorem}\label{thm:hcp2cp-bigtens}
  If $\seq{\mathcal{G}}$ in \hcp, then $\seq{\bigtens\mathcal{G}}$ in \cp.
\end{theorem}
\begin{proof}
  By case analysis on the structure of the hyper-environment $\ty{\mathcal{G}}$.
  \begin{itemize}
  \item
    If $\ty{\mathcal{G}} = \ty{\emptyhypercontext}$, we apply $(\one)$.
  \item
    If $\ty{\mathcal{G}} = \ty{\Gamma_1 \hsep \dots \hsep \Gamma_n}$,
    we apply \cref{lem:hcp-disentangle} to obtain proofs of $\seq{\Gamma_1}, \dots,
    \seq{\Gamma_n}$ in \cp, then we apply \cref{lem:cp-bigparr} to each of
    those proofs to obtain proofs of $\seq{\bigparr\Gamma_1}, \dots,
    \seq{\bigparr\Gamma_n}$, and join them using $(\tens)$ to obtain a single
    proof of $\seq{\bigtens\mathcal{G}}$ in \cp.
  \end{itemize}
\end{proof}
